draft_final_assignment

### 2022-11-28 draft_final_assingment.Rmd
Update draft_final_assingment.Rmd

```{r }
library(tidyverse)
library(quanteda)
library(quanteda.textstats)
library(readr)
library(dplyr)
library(quanteda.textplots)
library(uwot)
library(topicmodels)
library(tidytext)
library(ggrepel)
library(vader)
library(tidyr)
```

@@

#Wordcloud comparing Congresses
```{r }
dfmatCon <- dfm(corp, remove = stopwords("english"), remove_punct = TRUE, groups = corp$session) %>%
    dfm_trim(min_termfreq = 3)

>>>>

```{r }
library(tidyverse)
library(quanteda)
library(quanteda.textstats)
library(readr)
library(dplyr)
library(quanteda.textplots)
library(uwot)
library(topicmodels)
library(tidytext)
library(ggrepel)
library(vader)
library(tidyr)

@@

#Wordcloud comparing Congresses
```{r }
dfmatCon <- dfm(corp, remove = stopwords("english"), remove_numbers = TRUE, remove_punct = TRUE, groups = corp$session) %>%dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
  dfm_trim(min_termfreq = 3)
